---
title: "Project"
author: "Gabriele Cola - Nicholas LaRosa"
date: "2023-06-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 0. Library

```{r}
library(tidyverse)
library(igraph)
```

### 1. Import dataset

#### 1.1 Description of dataset

This is who-trusts-whom network of people who trade using **Bitcoin** on a platform called **Bitcoin Alpha**.\
Since Bitcoin users are **anonymous**, there is a need to maintain a record of users' reputation to prevent transactions with fraudulent and risky users.\
Members of Bitcoin Alpha rate other members in a scale of -10 (total distrust) to +10 (total trust) in steps of 1.\
This is the **weighted signed directed network** and we took from here the [dataset](%22https://snap.stanford.edu/data/soc-sign-bitcoin-alpha.html%22)

#### 1.2 Description of features

- **SOURCE**: node id of source (i.e rater)
- **TARGET**: node id of target (i.e ratee)
- **RATING**: the source's rating for the target, ranging from -10 to +10 in steps of 1
- **TIME**:   the time of the rating, measured as seconds since Epoch. 

```{r}
file_path <- "~/Downloads/newlab/Bitcoin_Network/soc-sign-bitcoinotc.csv"
# Import the CSV file
data <- read.csv(file_path, header = FALSE)

# Define custom column names
column_names <- c("SOURCE", "TARGET", "RATING", "TIME")

# Assign column names to the data frame
colnames(data) <- column_names
glimpse(data)

summary(data)

# we have to pre-process the time?

```

This graph is **weighted** and **directed**


### 2. Network Sampling

After or before we have to compute the network summary?

```{r}
# we have to put directed F or T ?
g<- graph_from_data_frame(data)#directed=FALSE)
n<- 500
gs<- induced_subgraph(g,sample(V(g),n))
```


### 3. Network Mapping
```{r}
# Which plot use?
plot(gs)
plot(gs, layout = layout.circle)
```

### 4.Network Charaterization

Comment on the results

```{r}
hist(degree(gs))
#degree_dist <- degree_distribution(gs)
clustering_coefficient <- transitivity(gs, type = "local")

s<- graph.strength(g)
b<- betweenness(g)
plot(s,b)
```


### 5. Network Models

```{r}

```

